---
title: "Data exploring"
author: "Matthew Phelps"
output: 
  rmdformats::readthedown:
    highlight: kate
---

```{r setup, include=FALSE}
library(ProjectTemplate)
library(knitr)
library(plotly)
opts_chunk$set(
  echo = FALSE,
  cache = TRUE,
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
)
opts_knit$set(width = 75)
opts_knit$set(root.dir = '..')

```

```{r, echo=FALSE, include=FALSE, cache=FALSE}

load.project()


```



# Outcome Summary

```{r}
n.groups <- dat$hjertestarter[, sum(at_risk)]
n.15 <- nrow(dat$hjertestarter[out_15ruter == 1])


```

Number of hjertestarter groups in total: `r n.groups`  
Number of groups acheiving 15 routes: `r n.15` (`r round(n.15 / n.groups * 100, digits = 1)`%)  


# Indsamler

The number of indsamler who signed up each day:
```{r, echo = FALSE}
ggbarplot(dat$indsamlerny[, .N, by = indtastings_date],
          x = "indtastings_date", y = "N",
          fill = "darkred",
          color = "white") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  xlab("Indtastings date")

```


The distribution of the mean lag time between successive indsamler signups for each group

```{r, echo = FALSE, warning=FALSE, message=FALSE}
gghistogram(dat$hjertestarter[!is.na(lag_mean)],
          x = "lag_mean",
          fill = "darkred",
          color = "white", bins = 40) +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  xlab("Mean time between sucessive registrations for hjertestarter groups")

```



The distribution of the mean number of days before d.day for indsamler signups for each group

```{r, echo = FALSE, warning=FALSE, message=FALSE}
gghistogram(dat$hjertestarter[!is.na(indtastings_mean)],
          x = "indtastings_mean",
          fill = "darkred",
          color = "white", bins = 40) +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  xlab("Mean indtastnings for hjertestarter groups (days before D-day)")
 
# DataExplorer::plot_correlation(dat$hjertestarter[!is.na(lag_mean), .(indtastings_mean, lag_mean)])

```



```{r}
n.groups <- 50
```

# Signups over time
Examine the registration over time among the hjertestarter groups that contained the first `r n.groups` indsamler to sign up
```{r}

indsamler.tmp <- dat$indsamlerny[hjertestarterid != 0]
setorder(indsamler.tmp, indtastningstidspunkt)
# Earliest signups by unique group id
tmp <- unique(indsamler.tmp, by = "hjertestarterid")[, .(hjertestarterid)]
obs <- nrow(tmp)

first.groups <- indsamler.tmp[hjertestarterid %in% tmp[1:n.groups, hjertestarterid]]
last.groups <- indsamler.tmp[hjertestarterid %in% tmp[(obs-n.groups):obs, hjertestarterid]]

p <-
  ggplot(
    first.groups,
    aes(
      x = indtastningstidspunkt,
      y = reg_order,
      group = hjertestarterid,
      color = as.factor(out_15ruter)
    )
  ) + geom_line(alpha = 0.5) +
  geom_point(alpha = 0.5, size = 0.3) + geom_hline(aes(yintercept = 15)) + theme_classic() +
  scale_color_manual(name = "Legend", labels = c("<15", "15+"), values = c("darkorange", "steelblue")) +
  ylab("Number of indsamler in group")
ggplotly(p, tooltip = c("hjertestarterid", "reg_order"))
```

The same plot, but this time showing the registration timeline for those hjerterstarter groups who had the latest `r n.groups` indsamler to sign up

```{r}

p <-
  ggplot(
    last.groups,
    aes(
      x = indtastningstidspunkt,
      y = reg_order,
      group = hjertestarterid,
      color = as.factor(out_15ruter)
    )
  ) + geom_line(alpha = 0.5) +
  geom_point(alpha = 0.5, size = 0.3) + geom_hline(aes(yintercept = 15)) + theme_classic() +
  scale_color_manual(name = "Legend", labels = c("<15", "15+"), values = c("darkorange", "steelblue")) +
  ylab("Number of indsamler in group")
ggplotly(p, tooltip = c("hjertestarterid", "reg_order"))

```


This time plot based on a continuous outcome (number of routes), instead of the binary outcome (<15 or >=15 routes)


```{r}

```


