---
title: "Missing data"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
---


```{r knitr_init, echo=FALSE, cache=FALSE, include=FALSE}

library(ProjectTemplate)
library(knitr)
## Global options
options(max.print = "75")
opts_chunk$set(
  echo = FALSE,
  cache = TRUE,
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
)
opts_knit$set(width = 75)
opts_knit$set(root.dir = '..')




```

```{r, echo = FALSE, include = FALSE}
load.project()
```






# Missing data between datasets based on Indsamler ID


```{r}
# Find the missing data between datasets
inds_not_in_log <-
  dat$indsamlerny[!(indsamlerid %in% dat$indsamler_log$indsamlerid),]
log_not_in_inds <-
  dat$indsamler_log[!(indsamlerid %in% dat$indsamlerny$indsamlerid),]
rutes_not_in_log <-
  dat$ruter[!(indsamlerid %in% dat$indsamler_log$indsamlerid)]
rutes_not_in_inds <-
  dat$ruter[!(indsamlerid %in% dat$indsamlerny$indsamlerid)]
inds_not_in_rute <-
  dat$indsamlerny[!(indsamlerid %in% dat$ruter$indsamlerid)]
log_not_in_rute <-
  dat$indsamler_log[!(indsamlerid %in% dat$ruter$indsamlerid)]

```


 * There were `r nrow(inds_not_in_log)` indsamler ID that was in `indsamlerny` that was not in the `indsamler_log` dataset:
```{r, echo = FALSE}
knitr::kable(inds_not_in_log)
```
 
 * There were `r nrow(log_not_in_inds)` recrods in `indsamler_log`, that do not have a matching indsamler ID in `indsamlerny`
```{r, echo = FALSE}
knitr::kable(log_not_in_inds)
```


 * There were `r nrow(rutes_not_in_log)` recrods in `ruter`, that do not have a matching indsamler ID in `indsamler_log`
```{r, echo = FALSE}
knitr::kable(head(rutes_not_in_log[, .(ruteid, rutenr, indsamlerid)]))
```

* There were `r nrow(rutes_not_in_inds)` recrods in `ruter`, that do not have a matching indsamler ID in `indsamlerny`
```{r, echo = FALSE}
knitr::kable(head(rutes_not_in_inds[, .(ruteid, omraade, indsamlerid)]))
```

* There were `r nrow(inds_not_in_rute)` recrods in `indsamlerny`, that do not have a matching indsamler ID in `ruter`
```{r, echo = FALSE}
knitr::kable(inds_not_in_rute)
```


# Missing Data based on rute ID
```{r}

rutes_not_in_log <-
  dat$ruter[!(ruteid %in% dat$indsamler_log$ruteid)]
rutes_not_in_inds <-
  dat$ruter[!(ruteid %in% dat$indsamlerny$ruteid)]
inds_not_in_rute <-
  dat$indsamlerny[!(ruteid %in% dat$ruter$ruteid)]
log_not_in_rute <-
  dat$indsamler_log[!(ruteid %in% dat$ruter$ruteid)]

```


 * There were `r nrow(rutes_not_in_log)` recrods in `ruter`, that do not have a matching rute ID in `indsamler_log`
```{r, echo = FALSE}
knitr::kable(head(rutes_not_in_log[, .(ruteid, rutenr, indsamlerid)]))
```

* There were `r nrow(rutes_not_in_inds)` recrods in `ruter`, that do not have a matching rute ID in `indsamlerny`
```{r, echo = FALSE}
knitr::kable(head(rutes_not_in_inds[, .(ruteid, omraade, indsamlerid)]))
```

* There were `r nrow(inds_not_in_rute)` recrods in `indsamlerny`, that do not have a matching rute ID in `ruter`
```{r, echo = FALSE}
knitr::kable(inds_not_in_rute)
```
